Vragenlijst thesis evaluatie

### 2015-08-10 doc/template/chap-5.tex
Figuren in orde en nog andere dingen

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{../../doc/template/Images/DefFlipItt.png}
\caption{A representation of a FlipIt game where both players are playing periodically. Every move or flip is indicated by a blue or orange circle. The attacker is represented in orange and the defender is represented in blue. The blue and orange rectangles represent the amount of time the respective player is in control of the resource.}
\label{fig:FLipItDefault}
\end{figure}

>>>>

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{../../doc/template/Images/FlipBasic}
\caption{A representation of a FlipIt game where both players are playing periodically. Every move or flip is indicated by a green (dark grey) or orange (light grey) circle. The attacker is represented in orange and the defender is represented in green. The blue and orange rectangles represent which player is in control of the resource.}
\label{fig:FLipItDefault}
\end{figure}

### 2015-08-10 doc/template/nash.tex
Figuren in orde en nog andere dingen

For case 2.B this leads to the following deduction, which results in the same formula as for case 1 but with a small difference for the value of $\delta_{D}$: The function increases on $[0, \sqrt{2\delta_{A}k_{D} + d^{2}}]$ and is decreasing on $[\sqrt{2\delta_{A}k_{D} + d^{2}}, \infty]$. Because $\delta_{D} \geq \delta_{A}$ there is a maximum on $\delta_{D} = maximum \{ \delta_{A}, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $ or because $d+\delta_{A} \geq \delta_{D}$ there is also on $\delta_{D} = minimum \{ \delta_{A}+d, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $. \todo{beter uitschrijven, deltaD moet tussen die twee waarden liggen}\\

@@

It follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing if $\delta_{D}> \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$ and decreasing if $\delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$  \\

@@

It follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing if $\delta_{D} > \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$ and decreasing if $\delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$. This is the same result as in case 1.\\

@@

\subsubsection*{$\delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$} 
From case 1 and case 2.b above, it follows that the benefit is decreasing but positive, which means that the attacker will play as fast as he can. For case 2.a  $\delta_{D} \geq \delta_{A}$ is increasing. It follows that for this case the attacker's maximum benefit is achieved for $\delta_{A} = \sqrt{d k_{A}\delta_{D}}$.
. In this case the attacker's maximum benefit is reached at $\delta_{A} = \delta_{A} = \sqrt{dk_{A}\delta_{D}}$  .
\subsubsection*{$\delta_{D} = \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$} 
The benefit $\beta_{A}(\delta_{D},\delta_{A})=0$ for case 1 and case 2.b for all $\delta_{D}$ in $[0, \infty [$. For case 2.a it follows that the benefit is increasing. The attacker's maximum benefit is achieved at any $\delta_{A} $ in 
\subsubsection*{$\delta_{D} > \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$} 
For case 1 and case 2.b the benefit is increasing but non-positive. This means that the attacker won't play ($delta_{A} = \infty$).

This brings us to the following opt function for : \todo{juiste resultaten hier nog invullen}
From this analyses we can compute $opt_{D}(\delta_{A})$ for two different cases as:
 \begin{displaymath}
  opt_{A}(\delta_{D}) = \left\{
     \begin{array}{lr}
       \delta_{D}, & \delta_{A} < 2(k_{D} - d)\\
       \left[ 0, \delta_{D} \right],  & \delta_{A} = 2(k_{D} - d) \\
       0 & \delta_{A} > 2(k_{D} - d)
     \end{array}
   \right.
\end{displaymath}
\\

>>>>

For case 2.B this leads to the following deduction, which results in the same formula as for case 1 but with a small difference for the value of $\delta_{D}$: The function increases on $[0, \sqrt{2\delta_{A}k_{D} + d^{2}}]$ and is decreasing on $[\sqrt{2\delta_{A}k_{D} + d^{2}}, \infty]$. Because $\delta_{D} \geq \delta_{A}$ there is a maximum on $\delta_{D} = maximum \{ \delta_{A}, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $ or because $d+\delta_{A} \geq \delta_{D}$ there is also on $\delta_{D} = minimum \{ \delta_{A}+d, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $. %-Remark- \todo{beter uitschrijven, deltaD moet tussen die twee waarden liggen}\\

@@

It follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing and non-positive if $\delta_{D}> \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$ and decreasing and positive if $\delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$  \\

@@

It follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing and non-positif if $\delta_{D} > \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$ and decreasing and positive if $\delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$. This is the same result as in case 1.\\

@@

\subsubsection*{$\delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$} 
From case 1 and case 2.b above, it follows that the benefit is decreasing but positive, which means that the attacker will play as fast as he can. For case 2.a  $\delta_{D} \geq \delta_{A}$ is increasing. It follows that for this case the attacker's maximum benefit is achieved for $\delta_{A} = \sqrt{d k_{A}\delta_{D}}$.
. In this case the attacker's maximum benefit is reached at $\delta_{A} = \delta_{A} = \sqrt{dk_{A}\delta_{D}}$  .
\subsubsection*{$\delta_{D} = \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$} 
The benefit $\beta_{A}(\delta_{D},\delta_{A})=0$ for case 1 and case 2.b for all $\delta_{D}$ in $[0, \infty [$. For case 2.a it follows that the benefit is increasing. The attacker's maximum benefit is achieved at any $\delta_{A} $ in 
\subsubsection*{$\delta_{D} > \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}$} 
For case 1 and case 2.b the benefit is increasing but non-positive. This means that the attacker won't play ($\delta_{A} = \infty$). 
\\
~~\\
From this analyses we can compute $opt_{A}(\delta_{D})$ :

 \begin{displaymath}
  opt_{A}(\delta_{D}) = \left\{
     \begin{array}{lr}
       \sqrt{d k_{A}\delta_{D}}, & \delta_{D} > \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}\\
       \left[ \sqrt{d k_{A}\delta_{D}}, \infty\right],  & \delta_{D} = \dfrac{(\delta_{D}-d)^{2}}{2k_{A}} \\
       \infty & \delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}
     \end{array}
   \right.
\end{displaymath}
\\
